# Data Processing Software

### [R01_Marketing](https://github.com/bfuchs18/R01_Marketing)

-   R01_Marketing is a GitHub repository that contains a collection of scripts to process and analyze REACH data. The scripts in this repository use the software outlined below.
-   R01_Marketing can be cloned or downloaded from GitHub

### [dataREACHr](https://github.com/bfuchs18/dataREACHr) {#datareachr}

-   dataREACHr is an R package that contains functions to process and organize survey and task and phenotype data into BIDS
-   dataREACHr can be installed from GitHub in R using the devtools package:

```{r install-datareachr, eval = FALSE}
devtools::install_github("alainapearce/datareachr")
```

### [dataprepr](https://github.com/alainapearce/dataprepr)

-   dataprepr is an R package that contains functions to score a variety of validated questionnaires
    -   This is a dependency of [dataREACHr](#datareachr)
-   Dataprepr can be installed from GitHub in R using the devtools package:

```{r install-dataprepr, eval = FALSE}
devtools::install_github("alainapearce/dataprepr")
```

### [dcm2bids](https://unfmontreal.github.io/Dcm2Bids/3.1.1/) {#dcm2bids}

-   dcm2bids is a program that reorganizes NIfTI files into the Brain Imaging Data Structure (BIDS)
-   Data processing scripts expect dcm2bids to be loaded via a conda environment described in /bids/code/dcm2bids/dcm2bids.yml.

The conda env can be created from the yml file by running the following commands in a Bash terminal on Roar Collab

```{bash, eval = FALSE}
# if conda has not been initialized, may need to run this first and then close and reopen terminal
conda init bash 

# Navigate to yml file
cd /storage/group/klk37/default/R01_Marketing/bids/code/dcm2bids/

# Load anaconda
module load anaconda

# Create a conda environment based on yml file
## Note, this will create the conda env in a user-specific directory, so every user has to create their own environment
conda env create -f dcm2bids.yml

# activate environment
conda activate dcm2bids
```

### [pydeface](https://github.com/poldracklab/pydeface) {#pydeface}

-   pydeface is a tool to remove facial structure from (i.e., "deface") MRI images.
-   pydeface requires FSL
-   Data processing scripts expect pydeface to be loaded via a conda environment described in /bids/code/dcm2bids/dcm2bids.yml. See the [dcm2bids](#dcm2bids) section for details on how to create the conda environment.

### [FSL](https://fsl.fmrib.ox.ac.uk/fsl/fslwiki) {#fsl}

-   FSL is a library of analysis tools for FMRI, MRI and diffusion brain imaging data
-   FSL is available for all users on Roar Collab

```{bash, eval = FALSE}
module load fsl
```

### [mriqc](https://mriqc.readthedocs.io/en/stable/index.html) {#mriqc}

-   MRIQC extracts no-reference IQMs (image quality metrics) from structural (T1w and T2w) and functional MRI (magnetic resonance imaging) data.

A container with MRIQC version 24.0.0 was built by running the following command in a Bash terminal on Roar Collab

```{bash, eval = FALSE}
singularity build /storage/group/klk37/default/sw/mriqc-24.0.0.simg  docker://nipreps/mriqc:24.0.0
```

### [fmriprep](https://fmriprep.org/en/stable/outputs.html) {#fmriprep}

-   fMRIprep is a preprocessing software for MRI data
-   On Roar Collab, fMRIprep version 24.0.1 is available in a Singularity Container within /storage/group/klk37/default/sw/fmriprep-23.2.0.simg. By using this singularity container, we can use a version of fMRIprep that is not presently available to all users of Roar Collab.

The container was created by running the following command in a Bash terminal on Roar Collab

```{bash, eval = FALSE}
singularity build /storage/group/klk37/default/sw/fmriprep-24.0.1.simg docker://nipreps/fmriprep:24.0.1
```

-   Version 24.0.1 was selected for processing because it is (or was) the most recent version available. To use other versions, build another singularity container by specifying a different version number in the command above.

```{bash, eval = FALSE}

```

### [afni](https://afni.nimh.nih.gov/) {#afni}

-   Analysis of Functional NeuroImages (AFNI) is a software suite of programs and scripts to analyse and visualize MRI data
-   On Roar Collab, AFNI version XXX is available in a Singularity Container within /storage/group/klk37/default/sw/XXXX. By using this singularity container, we can use a version of AFNI that is not presently available to all users of Roar Collab.

The container was created by running the following command in a Bash terminal on Roar Collab

```{bash, eval = FALSE}

```
